\textbf{Specification: Designing a Virtual Security Layer for Cloud Content}

### 2015-09-29 tex/paper.tex
Added content about copy-on-write

\title{\textbf{Providing an Access Control Layer for Content Distribution Networks}}
\author{Lukas Klingsbo}

@@

\subsubsection{JSON-RPC}
Over http? WebSockets? 
\subsubsection{TODO: Insert persistent storage here}
    TODO: Write down related terminology, if any
\subsection{Abbreviations}

@@

@@

@@

\section{Resulting system}
\subsection{Scalability}

>>>>

\title{\textbf{Designing a Virtual Security Layer for Cloud Content}}
\author{Lukas Klingsbo}

@@

\subsubsection{REST}
Over http? WebSockets? 
\subsubsection{TODO: Insert persistent storage here}
    TODO: Write down related terminology, if any
\subsection{Abbreviations}

@@

\section{Related Work}
\subsection{Copy-on-Write}
This work relies heavily on the Copy-on-Write principle which was founded and used in the Mach kernel~\cite{COPYONWRITE}. 
Today Copy-on-Write is used in everything from file systems~\cite{BTRFS} to desktop compositors~\cite{COMPOSITOR}.

Its principle is that when processes share data in between each other, the data is not copied until one of the processes 
does changes to it. This is an optimisation as the processes does not have to send all of the related data that is in memory, 
rather they only have to send pointers to the data. After many Copy-on-Write's a complex structure can be built up, 
but it is possible to solve that structure~\cite{COPYONWRITE2}.

@@

\section{Model}
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{View}
A view is a group of files which can be changed independently of the view's parent.
A view can have subviews which are either automatically dependant on its parent and 
updated when the parent is updated or optionally updated or forked from its parent 
once their content diverge.

\subsubsection{Project}
A project is just a name for the view which is a root of a tree of views.
The system can contain several projects and their trees are completely disjoint.

\subsubsection{File}
A file refers to an actual physical file in the file system.

\subsubsection{Content}
Content is an asset contained in a view, it is a virtual file.
It could be described as a link between the view and the real file. 
It can be for example an image, video or binary blob combined with meta-data.

\subsubsection{User}
A user is the structure that handles people who has been granted access to the system.
Access to the system is handled by a separate service, like LDAP.

\section{Copy-on-Write}

@@

\section{Resulting system}
\subsection{REST Endpoints}
For the frontend to communicate with the backend REST is used, the following endpoints were configured:

\begin{itemize}
  \item projects
      \subitem GET - list all projects
      \subitem POST - create new project
  \item projects/\{id\}
      \subitem GET - get specific project
      \subitem PUT - update existing project
      \subitem DELETE - delete existing project
  \item projects/\{id\}/content
      \subitem GET - list all content in a specific project
      \subitem POST - create new content in a specific project 
  \item projects/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific project
      \subitem PUT - update existing content in a specific project
      \subitem DELETE - delete existing content in a specific project

  \item projects/\{id\}/views
      \subitem GET - list all views in a specific project
      \subitem POST - create new view in a specific project 
  \item projects/\{id\}/views/\{id\}
      \subitem GET - get specific view in a specific project
      \subitem PUT - update existing view
      \subitem DELETE - delete existing view
  \item projects/\{id\}/views/\{id\}/content
      \subitem GET - list all content in a specific view
      \subitem POST - create new content in a specific view 
  \item projects/\{id\}/views/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific view
      \subitem PUT - update existing content in a specific view
      \subitem DELETE - delete existing content in a specific view
\end{itemize}

\subsection{Scalability}

### 2015-09-29 tex/spec.tex
Added content about copy-on-write

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Background}
This work will be done at the company Uprise (Dragarbrunnsgatan 36C, Uppsala). 
The goal of this project is to design and develop a local access control layer 
for files, projects and views in a content distribution network.
This should make handling of content safer and make it easier to have control 
over the security settings of projects and groups of files and will also make 
it possible to enforce local (as in not on the CDN) auth and audit logging.

@@

It should also be possible to create so called views and projects which a group 
of files are added to, which then have their own security settings.
A file can be a part of several views that then in their turn have different 
security settings. The system should then be able to determine what the correct 
security setting for the actual file is.

For example, which security rules should take precedence if a file, lets call it 
``Test.jpg'', is uploaded to a CDN once, but is contained in two views or projects 
with different security settings. If then Test.jpg is changed in one of the projects, 
but is not supposed to be changed in the other, how is that handled and how is 
it determined when a change should propagate through the whole system or when it 
should just create a new version of it in the current virtual view or project.
\vspace{12pt}
\\
More things to examine:
\begin{itemize}
    \item A way to dynamically switch a single or a group of files security settings has 
to be examined as the storage method of the files usually will be distributed.
    \item To make sure you are handling the correct file previews has to be shown in the system.
    \item Access to the system should be configured in a modular sense, one module could be 
LDAP.
\end{itemize}

@@

\newpage
\section{Methods}
\begin{itemize}
  \item The design will be well evaluated in the sense of security and technical usability.
  \item The prototype/system will be developed in Scala and React. 
  \item A literature study will be done once the specification is accepted. 
  \item Results will be evaluated from a security and scalability point of view. 
  \item A work station and desk space will be provided by Uprise.
\end{itemize}

@@

It is possible to do delimitation of the core research question as the project 
proceeds, but it will most likely not be needed as the research question is 
quite concise.

\newpage
\section{Time Plan}
Note that this is just a rough time plan that will change during the course of 
the project when the circumstances change.
There will rarely be one task at a time, but rather a lot of the tasks will be 
overlapping.
\begin{itemize}
  \item A few days - Properly setting up the work station
  \item 2 weeks - Literature study and obtaining relevant books etc
  \item 20 weeks - Writing the report should be done pretty much 
  throughout the whole project
  \item 1 week - Analyze the current system for managing the CDN assets
  \item 1 week - Analyze what has been done earlier regarding the 
  subject and determine if anything is useful for this project
  \item 4 weeks - Implement a prototype
  \item 1 week - Scalability testing
  \item 3 weeks - Security testing
\end{itemize}

>>>>

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Background}
This work will be done at the company Uprise (Dragarbrunnsgatan 36C, Uppsala). 
The goal of this project is to design and develop a local access control layer 
for files and views in a content distribution network.
This should make handling of content safer and make it easier to have control 
over the security settings of groups of files and will also make 
it possible to enforce local (as in not on the CDN) auth and audit logging.

@@

It should also be possible to create so called views which a group 
of files are added to, which then have their own security settings.
A view is a subset of files, and a view can be a view of another view and then 
only contain files which is in contained in the parent view. 
A file can be a part of several views that then in their turn have different 
security settings. The system should then be able to determine what the correct 
security setting for the actual file is or if it needs to create several versions 
of the file.

For example, which security rules should take precedence if a file, lets call it 
``Test.jpg'', is uploaded to a CDN once, but is contained in two views 
with different security settings. If then Test.jpg is changed in one of the views, 
but is not supposed to be changed in the other, how is that handled and how is 
it determined when a change should propagate through the whole system or when it 
should just create a new version of it in the current virtual view.
\vspace{12pt}
\\
More things to examine:
\begin{itemize}
    \item A way to dynamically switch a single or a group of files security settings has 
to be examined as the storage method of the files usually will be distributed.
    \item To make sure you are handling the correct file previews has to be shown in the system.
    \item Access to the system should be configured in a modular sense, one module could be 
LDAP.
\end{itemize}

@@

\newpage
\section{Methods}
\begin{itemize}
  \item The design will be well evaluated in the sense of security and technical usability
  \item The prototype/system will be developed in Scala and React
  \item A literature study will be done to find more relevant litterature once the specification is accepted 
  \item The proof should be an informal paper proof or if time is sufficient a proper proof should be done in a model checker
  \item Results from the informal proof will be evaluated and documented
  \item The implementation will be evaluated with existing security tools, it needs to be researched which these tools will be
      \item Results from these tools and that are relevant to the report will be added in an appendix
  \item Everything relevant in the work process, from problems that occured to final results, will be documented in the report
  \item The code will have its own documentation separated from the report 
  \item The prototype/system will be released under an open source license
  \item A work station and desk space will be provided by Uprise
\end{itemize}

@@

It is possible to do delimitation of the core research question as the project 
proceeds, but it will most likely not be needed as the research question is 
quite concise.
\newpage
\section{Time Plan}
Note that this is just a rough time plan that will change during the course of 
the project when the circumstances change.
There will rarely be one task at a time, but rather a lot of the tasks will be 
overlapping.
\begin{itemize}
  \item A few days - Properly setting up the work station
  \item 2 weeks - Literature study and obtaining relevant books etc
  \item 20 weeks - Writing the report should be done pretty much 
  throughout the whole project
  \item 1 week - Analyze the current system for managing the CDN assets
  \item 1 week - Analyze what has been done earlier regarding the 
  subject and determine if anything is useful for this project
  \item 3 weeks - Define system mechanism and model
  \item 3 weeks - Analyse system mechanism and model (this item will overlap with the definition)
  \item 3 weeks - Informal proof (or formal if time is sufficient) of the systems mechanism and model
  \item 8 weeks - Implement a prototype/system
      \subitem 1 week - defining and developing backend API
      \subitem 2 weeks - define a basic set of extendable security rules
      \subitem <1 week - investigate and implement "physical" file handler
      \subitem <1 week - implement simple persistant storage for meta data
      \subitem 1-2 weeks - implement authentication interface
      \subitem <1 week - implement CDN interface
      \subitem 2 weeks - implement user interface
  \item 1 weeks - Test security of implementation, if only a prototype is developed the security should only be analysed in theory
\end{itemize}

The interfaces does not have to have anything real connected to them, it just needs 
to be possible to hook up services to them.
